Homicide Increases in the COVID-19 Era

### 2025-03-01 Draft2.qmd
Update Draft2.qmd

>>>>

## Time series analyzing homicide rate trends over time by socioeconomic quartiles

```{r, echo=FALSE}
# Data Preparation
homicides <- crime_la %>% inner_join(crimes_with_zips, by = "crime_id") %>% filter(offense_type == "HOMICIDE") %>% mutate(date = as.Date(date)) 
homicides <- homicides %>% left_join(cali_median_income, by = c("zip_code" = "ZCTA"))
homicides$median_income <- as.numeric(homicides$median_income)

# Form income quartiles
homicides <- homicides %>% mutate(income_quartile = ntile(median_income, 4)) 
homicide_trends <- homicides %>% mutate(year = lubridate::year(date)) %>% group_by(year, income_quartile) %>% summarize(homicide_count = n(), .groups = "drop")

# Plot homicide trends over time by income quartile
ggplot(homicide_trends, aes(x = year, y = homicide_count, color = factor(income_quartile))) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  labs(
    x = "Year",
    y = "Number of Homicides",
    color = "Income Quartile"
  ) +
  theme_minimal()
```
